% Conclusion v3
\section{Conclusion}
\label{sec:conclusion}

\subsection{Summary}

A unified framework connecting correctness, robustness, and stability.
The Synthesis Theorem: when $\mathrm{DoF}(P)=(0,0,0)$, all three coincide.
The equivalence is structural collapse, not assumption.

\subsection{Boundary}

$\mathrm{UES}(P)\neq\emptyset$ is the precise boundary condition.
$\mathrm{DoF}_{\mathrm{src}}>0$ is computable and verifiable.

\subsection{Known limitations}

\paragraph{Cross-community validation.} Not yet reviewed by all three disciplines.

\paragraph{DoF completeness.} Measurement DoF and categorical DoF candidates not fully analyzed.

\paragraph{AI-assisted development.}
All technical claims should be verified against sealed/hardened source documents.

\subsection{Final remark}

\begin{quote}\itshape
The synthesis theorem is not an accidental equivalence.
It is a collapse induced by the elimination of all degrees of freedom.
\end{quote}

\section*{Acknowledgments}

This research was developed with substantial assistance from multiple
AI systems: Claude (Anthropic), used primarily for formalization of
definitions, proof sketching, LaTeX structuring, and adversarial review
simulation; ChatGPT (OpenAI), used for literature search, conceptual
cross-checking, and alternative framing of arguments; and Perplexity AI,
used for real-time verification of on-chain data and governance
documentation cited in Section~\ref{sec:defi-empirical}.

All mathematical claims are the responsibility of the author.
