\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{geometry}
\geometry{margin=1in}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Assumption}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\At}{\mathrm{At}}
\newcommand{\SC}{\mathrm{SC}_T}
\newcommand{\Cmin}{C_{\min}}
\newcommand{\Stable}{\mathrm{Stable}_{\mathcal{A}}}
\newcommand{\DoF}{\mathrm{DoF}}
\newcommand{\UES}{\mathrm{UES}}
\newcommand{\SCSet}{\mathrm{SCSet}}
\newcommand{\Break}{\mathrm{Break}}
\newcommand{\Cert}{\mathrm{Cert}}
\newcommand{\Enc}{\mathrm{Enc}}
\newcommand{\Dcomp}{D_{\mathrm{comp}}}
\newcommand{\CertReach}{\mathrm{CertReach}}
\newcommand{\UnbreakSet}{\mathrm{UnbreakSet}}

\title{When Correctness, Robustness, and Stability Coincide\\
  {\large A Unified Framework via Degrees of Freedom and Structural Collapse}}
\author{Hai Hai Fu}
\date{2026}

\begin{document}
\maketitle

\begin{abstract}
We present a unified framework connecting logical correctness,
adversarial robustness, and dynamic stability.
Using a minimal language based on states, rule closure, break structures,
and system dynamics, we show that these notions coincide under precise
structural conditions.

We prove that a state is canonical if and only if it is unbreakable
and dynamically stable, provided the system admits full certificate
coverage and contains no unavoidable external inputs.
This equivalence is characterized by the vanishing of all
degrees of freedom---representation, source, and dynamic---and is
not assumed but arises as a structural consequence.

We identify the exact boundary at which this collapse fails and develop
a quantitative robustness theory for open systems.
In such settings, robustness is governed by finite break costs and is
often dominated by execution-layer vulnerabilities rather than
governance or protocol design.

The framework yields a unified interpretation across logic, security,
and dynamical systems, and provides practical tools for analyzing
real-world protocols.
Empirical verification against three DeFi protocols (Aave, Compound, Sky)
confirms that all observed instability events are instances of
$\DoF_{\mathrm{src}} > 0$ materialized without an explicit adversary.
\end{abstract}

\tableofcontents
\newpage

\section{Introduction}
\label{sec:intro}
\input{latex/introduction}

\input{latex/minimal_core}
\input{latex/unified_language}
\input{latex/expressivity}
\input{latex/dof_synthesis}
\input{latex/boundary_cot}
\input{latex/mlr_el}
\input{latex/defi_verification}
\input{latex/related_work}
\input{latex/conclusion}
\input{latex/appendix_bridge}

\bibliographystyle{plain}
\bibliography{latex/refs}

\end{document}
